---
title: "Assignment 10"
author: Artie Maharaj
date: April 21, 2020
output: html_notebook
---
This is assignment 10 for EDRM 718

1. Write a script to import and tidy the Johnson Elementary Project Data
```{r}
library(tidyverse)

johnson_data <- read_csv("Johnson Elementary ELA Project.csv") 

johnson_data <- read_csv("Johnson Elementary ELA Project.csv", skip =4,         
col_names = c("Room", "Student ID", "TardiesAbsences", "1st Quarter", "2nd Quarter", "3rd Quarter", "4th Quarter"), 
                         col_types = cols("Room" = col_factor()))

johnson_data <- as_tibble(johnson_data)

johnson_data

new_johnson_data <- johnson_data %>%
  separate(TardiesAbsences, into = c("Tardies", "Absences"),convert = TRUE)

new_johnson_data <-as_tibble(new_johnson_data)

new_johnson_data <- new_johnson_data %>%
  fill(Room)

tidy_johnson_data <- new_johnson_data[-c(1, 22,45,69,93,116,154,175,196),]
tidy_johnson_data <- as_tibble(tidy_johnson_data)
```

2. Write a script to provie summary statistics for the number of tardies and absences for each room. 
```{r}

tidy_johnson_data %>%
  group_by(Room) %>%
   summarize(count = n(),
   Average_Tardies = mean(Tardies, na.rm = TRUE),
   Average_Absences = mean(Absences, na.rm = TRUE))


```

3. Write a script to show the frequency of missing data points for each quarter by room.

```{r}
tidy_johnson_data %>%
group_by(Room) %>%
summarize(na_q1 = sum(is.na(`1st Quarter`)),
          na_q2 = sum(is.na(`2nd Quarter`)),
          na_q3 = sum(is.na(`3rd Quarter`)),
          na_q4 = sum(is.na(`4th Quarter`)))
```

4. Construct a graph that illustrates the median rating trends across the four quarters for the fifth-grade classes
```{r}

tidy_johnson_data %>%
group_by(Room)%>%
summarize(Q1_median = median(`1st Quarter`, na.rm = TRUE),
            Q2_median = median(`2nd Quarter`, na.rm = TRUE),
            Q3_median = median(`3rd Quarter`,na.rm = TRUE),
            Q4_median = median(`4th Quarter`,na.rm = TRUE))

medians <- sum(Q1_median, Q2_median, Q3_median, Q4_median)
  
  ggplot(aes(x = Room, y = medians)) +
    geom_point(aes(size = count)) +
    geom_smooth(se = FALSE)

  
```


5. Use the NYC flights data to construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from New York City to Atlanta. Your graph should include a title and easy to read labels, including names of airlines rather than airline codes. 

```{r}

```

