---
title: "Assignment 10"
author: Artie Maharaj
date: April 21, 2020
output: html_notebook
---
This is assignment 10 for EDRM 718


1. Write a script to import and tidy the Johnson Elementary Project Data
```{r}
library(tidyverse)

johnson_data <- read_csv("Johnson Elementary ELA Project.csv") 

johnson_data <- read_csv("Johnson Elementary ELA Project.csv", skip =5,           col_names = c("Room", "Student ID", "TardiesAbsences", "1st 
Quarter", "2nd Quarter", "3rd Quarter", "4th Quarter"), 
                         col_types = cols("Room" = col_factor()))

johnson_data <- as_tibble(johnson_data)

johnson_data

new_johnson_data <- johnson_data %>%
  separate(TardiesAbsences, into = c("Tardies", "Absences"),convert = TRUE)

new_johnson_data <-as_tibble(new_johnson_data)
new_johnson_data

```

2. Write a script to provie summary statistics for the number of tardies and absences for each room. 
```{r}

```

3. Write a script to show the frequency of missing data points for each quarter by room.

```{r}

```


4. Construct a grpah that illustrates the median rating trends across the four quarters for the fifth-grade classes
```{r}

```


5. Use the NYC flights data to construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from New York City to Atlanta. Your graph should include a title and easy to read labels, including names of airlines rather than airline codes. 

```{r}

```

