---
title: "Assignment 10"
author: Artie Maharaj
date: April 21, 2020
output: html_notebook
---
This is assignment 10 for EDRM 718

1. Write a script to import and tidy the Johnson Elementary Project Data
```{r}
library(tidyverse)

johnson_data <- read_csv("Johnson Elementary ELA Project.csv") 

johnson_data <- read_csv("Johnson Elementary ELA Project.csv", skip =4,         
col_names = c("Room", "Student ID", "TardiesAbsences", "1st Quarter", "2nd Quarter", "3rd Quarter", "4th Quarter"), 
                         col_types = cols("Room" = col_factor()))

johnson_data <- as_tibble(johnson_data)

johnson_data

new_johnson_data <- johnson_data %>%
  separate(TardiesAbsences, into = c("Tardies", "Absences"),convert = TRUE)

new_johnson_data <-as_tibble(new_johnson_data)

new_johnson_data <- new_johnson_data %>%
  fill(Room)

tidy_johnson_data <- new_johnson_data[-c(1, 22,45,69,93,116,154,175,196),]

tidy_johnson_data <- as_tibble(tidy_johnson_data)
  
tidy_johnson_data <- tidy_johnson_data %>%
  gather(`1st Quarter`, `2nd Quarter`, `3rd Quarter`, `4th Quarter`,    
         key = "Quarter",
         value = "Ratings")

tidy_johnson_data
```

2. Write a script to provie summary statistics for the number of tardies and absences for each room. 
```{r}
tidy_johnson_data %>%
  group_by(Room) %>%
   summarize(count = n(),
   Average_Tardies = mean(Tardies, na.rm = TRUE),
   sd_Tardies = sd(Tardies, na.rm = TRUE),
   min_Tardies = min(Tardies, na.rm = TRUE),
   max_Tardies = max(Tardies, na.rm = TRUE),
   median_Tardies = median(Tardies, na.rm = TRUE),
   first.quantile_Tardies = quantile(Tardies, probs = .25, na.rm = TRUE),
   third.quantile_Targies= quantile(Tardies, probs =.75, na.rm = TRUE),
   median_Absences = mean(Absences, na.rm = TRUE),
   Average_Absences = mean(Absences, na.rm = TRUE),
   sd_Absences = sd(Absences, na.rm = TRUE),
   min_Absences = min(Absences, na.rm = TRUE),
   max_Absences = max(Absences, na.rm = TRUE),
   first.quantile_Absences = quantile(Absences,probs = .25, na.rm =TRUE),
   third.quantile_Absences = quantile(Tardies, probs =.75, na.rm = TRUE))
```

3. Write a script to show the frequency of missing data points for each quarter by room.

```{r}
johnson.missing <- tidy_johnson_data %>%
  group_by(Room, Quarter) %>%
  summarize(sum(is.na(Ratings)))

```

4. Construct a graph that illustrates the median rating trends across the four quarters for the fifth-grade classes
```{r}

tidy_johnson_data %>%
  group_by(Room) %>%
  summarize(count = n(),
            median_rating = median(Ratings, na.rm = TRUE)) %>%
  ggplot(aes(x = Quarter, y = median_rating, color = Room, na.rm = TRUE)) +
    geom_line() +
    labs(x = "Quarter",
     y = "Median Ratings")

```


5. Use the NYC flights data to construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from New York City to Atlanta. Your graph should include a title and easy to read labels, including names of airlines rather than airline codes. 

```{r}

flights <- read_csv("NYC Flights 2013.csv")

arrive.proportion <- flights%>%
  filter(dest == "ATL")%>%
  mutate(at.proportion = sched_arr_time/arr_time, na.rm= TRUE) %>%
  select(carrier, origin, dest, sched_arr_time, arr_time, at.proportion) 


arrive.proportion %>%
  group_by(carrier) %>%
  ggplot(arrive.proportion, aes(x = at.proportion, fill(carrier))) +
  geom_bar(position = "fill") +
  labs(title = "Proportion of 2013 flights that arrived on time by Airline        from NYC to ATL",
        x = "Proportion", y = "Airline")


```

